### 2016-09-28 Theorem1_FP.tex
Syntax consistency of proof1

\begin{proof}[\Cref{thm1}]
The proof of the theorem will use a game playing argument as shown in \Cref{fig:Game}. $\game{0}(A)$ exactly simulates $\ExpCorrect{\Pi_\mathrm{lin},\distr{\calS}{},r}{A}$ with hash functions $h_j(x) =  F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$. So,

@@

 In $\game{1}(A)$, $F_{K_1}$ is replaced by a random function, whereas in $\game{2}(A)$, both $F_{K_0}$ and $F_{K_1}$ are replaced by random functions.

%\caption{Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
\begin{figure}
\fpage{0.9}{
\hpagessl{0.5}{0.5}
{
$\adversaryv{B_1^{\calO}}$\\
$S \getsr \distr{\calS}{}$\\
$\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
Run~$A(S, \pubaux)$\\
When $A$ asks $\TestOracle(q_x)$:\\
\nudge if $q_x \in \mathcal{C}$ then Return $\bot$\\
\nudge $\calC \gets \calC \cup \{q_x\}$\\
\nudge $a \gets \Qry^{\HashOracle}(\pubaux,\privaux,q_x)$\\
\nudge if $a \neq q_x(S)$ then \\
\nudge \nudge $\err \gets \err + 1$\\
\nudge Return~$a$\\
When $A$ halts: \\
\nudge if $\err  < r$ then Return 0\\
\nudge Return 1\\\\
%
\oracle{$\HashOracle(x)$}\\
Return $F_{K_1}(x) + i\cdot \calO(x)$, for $i\in[1,k]$\\
}
{
$\adversaryv{B_2^{\calO}}$\\
$S \getsr \distr{\calS}{}$\\
$\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
Run~$A(S, \pubaux)$\\
When $A$ asks $\TestOracle(q_x)$:\\
\nudge if $q_x \in \mathcal{C}$ then Return $\bot$\\
\nudge $\calC \gets \calC \cup \{q_x\}$\\
\nudge $a \gets \Qry^{\HashOracle}(\pubaux,\privaux,q_x)$\\
\nudge if $a \neq q_x(S)$ then \\
\nudge \nudge $\err \gets \err +1$\\
\nudge Return~$a$\\
When $A$ halts: \\
\nudge if $\err  < r$ then Return 0\\
\nudge Return 1\\\\
\oracle{$\HashOracle(x)$}\\
$a \getsr [m]$\\
if $T[x] \neq \undefined$\\
\nudge $a \gets T[x]$\\
$T[x] \gets a$\\
Return  $\calO(x) + i\cdot a$, for $i\in[1,k]$
}
}
\caption{\Cref{thm1}:Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
\end{figure}

@@

%\caption{Game playing argument}\label{fig:Game}
\begin{figure}
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{\game{0}(A)}\\
$S \getsr \distr{\calS}{}$; $\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\
%
\oracle{$\TestOracle(q_x)$}\\
if $q_x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup \{q_x\}$\\
$a \gets \Qry^{\HashOracle}(\pubaux,\privaux,q_x)$\\
if $a \neq q_x(S)$ then $\err \gets \err + 1$\\
Return~$a$\\
%
\oracle{$\HashOracle(x)$}\\
for $i = 1$ to $k$\\
\nudge $h_i(x) = F_{K_1}(x)+i \cdot F_{K_2}(x) \bmod m$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{\game{1}(A)}\\
$\rho \getsr \Func{\univ,[m]}$\\
$S \getsr \distr{\calS}{}$; $\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\
%
\oracle{$\TestOracle(q_x)$}\\
if $q_x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup \{q_x\}$\\
$a \gets \Qry^{\HashOracle}(\pubaux,\privaux,q_x)$\\
if $a \neq q_x(S)$ then $\err \gets \err + 1$\\
Return~$a$\\
%
\oracle{$\HashOracle(x)$}\\
for $i=1$ to $k$\\
\nudge $h_i(x) = F_{K_1}(x)+i \cdot \rho(x) \bmod m$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
}
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{\game{2}(A)}\\
$\rho_1,\rho_2 \getsr \Func{\univ,[m]}$\\
$S \getsr \distr{\calS}{}$; $\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\
%
\oracle{$\TestOracle(q_x)$}\\
if $q_x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup \{q_x\}$\\
$a \gets \Qry^{\HashOracle}(\pubaux,\privaux,q_x)$\\
if $a \neq q_x(S)$ then $\err \gets \err + 1$\\
Return~$a$\\\\
%
\oracle{$\HashOracle(x)$}\\
for $i=1$ to $k$\\
\nudge $h_i(x) = \rho_1(x)+i \cdot \rho_2(x) \bmod m$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{{$\game{3}(A)$},\fbox{$\game{4}(A)$}}\\
$c\gets 0$, $\bad \gets \false$, $\err \gets 0$;  $\calC \gets \emptyset$\\
$S \getsr \distr{\calS}{}$; $\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\bad = \true$ then \fbox{Return 0}\\
if $\err  < r$ then Return 0\\
Return 1\\
%
\oracle{$\TestOracle(q_x)$}\\
if $q_x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup \{q_x\}$\\
$c \gets c+1$\\
$v \gets \Qry^{\HashOracle}(\pubaux,\privaux,q_x)$\\
if $c \in \mathcal{I}$ and $v = q_x(S)$ then \\
\nudge $\bad \gets \true$ \\
if $c \not\in \mathcal{I}$ and $v \neq q_x(S)$ then \\
\nudge $\bad \gets \true$\\
if $v \neq q_x(S)$ then $\err \gets \err +1$\\
Return~$v$\\
%
\oracle{$\HashOracle(x)$}\\
$a,b \getsr [m]$\\
for $i = 1$ to~$k$\\
\nudge $v_i = a+i \cdot b \bmod m$\\
Return $\left(v_1,\ldots,v_k\right)$
}
}
\caption{\Cref{thm1}: Game playing argument}\label{fig:Game}
\end{figure}

%\caption{PRF game}\label{fig:prf}
\begin{figure}
\centering
\fpage{0.45}{
\hpagess{0.4}{0.35}
{
$\experimentv{\ExpPRF{F}{B}}$\\
$K \getsr \calK $\\
$\rho \getsr \Func{\univ,[m]}$\\
$b \getsr \bits$\\
$b' \getsr B^\calO$\\
Return $[b = b']$\\
}
{
$\oracle{\calO \smallskip(x)}$\\
if $ b = 1$ then\\
\nudge Return $F_K(x)$\\
Return $\rho(x)$\\
}
}
\caption{PRF security notion}\label{fig:prf}
\end{figure}

%\caption{Non-adaptive adversary $D$ simulating $\game{4}(A)$} \label{fig:D}
\begin{figure}
\centering
\fpage{0.35}
{
$\adversaryv{D(S, \pubaux)}$\\[4pt]
$c \gets 0$\\%, $\calX \gets \emptyset$\\
$\calC \gets \emptyset$; $\err \gets 0$\\
$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
Run $A(S, \pubaux)$\\
When $A$ asks $\TestOracle(q_x)$:\\
\nudge if $q_x \in \mathcal{C}$ then Return $\bot$\\
\nudge $\calC \gets \calC \cup \{q_x\}$\\
\nudge $c \gets c+1$\\
\nudge $r \gets 0$\\
\nudge if $c \in \mathcal{I}$\\
\nudge \nudge $r \gets 1$\\
\nudge \nudge $\err \gets \err + 1$\\
\nudge Return $r$\\
When $A$ halts:\\
\nudge Return $\bot$
}
\caption{Zero-query adversary $D$} \label{fig:D}
\end{figure}

>>>>

%F_{K}(\langle 1,x \rangle) + j\cdot F_{K}(\langle 2,x \rangle) \bmod m
\begin{proof}[\Cref{thm1}]
The proof of the theorem will use a game playing argument as shown in \Cref{fig:Game}. $\game{0}(A)$ exactly simulates $\ExpCorrect{\Pi_\mathrm{lin},\distr{\calS}{},r}{A}$ with hash functions $h_j(x) =  F_{K}(\langle 1,x \rangle) + j\cdot F_{K}(\langle 2,x \rangle) \bmod m$. So,

@@

 In $\game{1}(A)$, $F_{K}(\langle 1,\cdot \rangle)$ is replaced by a random function, whereas in $\game{2}(A)$, both $F_{K}(\langle 1,\cdot \rangle)$ and $F_{K}(\langle 2, \cdot \rangle)$ are replaced by random functions.

%\caption{Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
\begin{figure}
\fpage{0.9}{
\hpagessl{0.5}{0.5}
{
$\adversaryv{B_1^{\calO}(S, \pubaux)}$\\
%$S \getsr A$\\
$\calC \gets \emptyset$; $\err \gets 0$\\
%$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
Run~$A(\pubaux)$\\
When $A$ asks $\TestOracle(\qry_x)$:\\
\nudge if $x \in \mathcal{C}$ then Return $\bot$\\
\nudge $\calC \gets \calC \cup x$\\
\nudge $a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
\nudge if $a \neq \qry_x(S)$ then \\
\nudge \nudge $\err \gets \err + 1$\\
\nudge Return~$a$\\
When $A$ halts: \\
\nudge if $\err  < r$ then Return 0\\
\nudge Return 1\\\\
%
\oracle{$\HashOracle(x)$}\\
for $i \in \{1,2,\ldots,k\}$\\
\nudge $v_i \gets F_{K}(\langle 1,x \rangle) + i \cdot \calO(\langle 2,x \rangle) \bmod m$\\
Return ${v_1,v_2,\ldots,v_k}$
}
{
$\adversaryv{B_2^{\calO}(S, \pubaux)}$\\
%$S \getsr A$\\
$\calC \gets \emptyset$; $\err \gets 0$\\
%$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
Run~$A(\pubaux)$\\
When $A$ asks $\TestOracle(\qry_x)$:\\
\nudge if $x \in \mathcal{C}$ then Return $\bot$\\
\nudge $\calC \gets \calC \cup x$\\
\nudge $a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
\nudge if $a \neq \qry_x(S)$ then \\
\nudge \nudge $\err \gets \err +1$\\
\nudge Return~$a$\\
When $A$ halts: \\
\nudge if $\err  < r$ then Return 0\\
\nudge Return 1\\\\
%
\oracle{$\HashOracle(x)$}\\
$a \getsr [m]$\\
if $T[x] \neq \undefined$\\
\nudge $a \gets T[x]$\\
$T[x] \gets a$\\
for $i \in \{1,2,\ldots,k\}$\\
\nudge $v_i \gets \calO(\langle 1,x \rangle) + i\cdot a$\\
Return ${v_1,v_2,\ldots,v_k}$
}
}
\caption{\Cref{thm1}:Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
\end{figure}

@@

%\caption{Game playing argument}\label{fig:Game}
\begin{figure}
\fpage{.99}{
\hpagessl{.52}{.5}
{
\underline{\game{0}(A)}\\
$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\
%
\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
$a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
if $a \neq \qry_x(S)$ then $\err \gets \err + 1$\\
Return~$a$\\
%
\oracle{$\HashOracle(x)$}\\
for $i = 1$ to $k$\\
\nudge $h_i(x) = F_{K}(\langle 1,x \rangle) + i\cdot F_{K}(\langle 2,x \rangle) \bmod m$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{\game{1}(A)}\\
$K \getsr \calK$, $\rho \getsr \Func{\univ,[m]}$\\
$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\
%
\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
$a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
if $a \neq \qry_x(S)$ then $\err \gets \err + 1$\\
Return~$a$\\
%
\oracle{$\HashOracle(x)$}\\
for $i=1$ to $k$\\
\nudge $h_i(x) = F_{K}(\langle 1,x \rangle) + i \cdot \rho(x) \bmod m$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
}
\fpage{.99}{
\hpagessl{.52}{.5}
{
\underline{\game{2}(A)}\\
$\rho_1,\rho_2 \getsr \Func{\univ,[m]}$\\
$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\
%
\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
$a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
if $a \neq \qry_x(S)$ then $\err \gets \err + 1$\\
Return~$a$\\\\
%
\oracle{$\HashOracle(x)$}\\
for $i=1$ to $k$\\
\nudge $h_i(x) = \rho_1(x) + i \cdot \rho_2(x) \bmod m$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{{$\game{3}(A)$},\fbox{$\game{4}(A)$}}\\
$c\gets 0$, $\bad \gets \false$, $\err \gets 0$;  $\calC \gets \emptyset$\\
$S \getsr A$; $\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(\pubaux)$\\
if $\bad = \true$ then \fbox{Return 0}\\
if $\err  < r$ then Return 0\\
Return 1\\
%
\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
$c \gets c+1$\\
$v \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
if $c \in \mathcal{I}$ and $v = \qry_x(S)$ then \\
\nudge $\bad \gets \true$ \\
if $c \not\in \mathcal{I}$ and $v \neq \qry_x(S)$ then \\
\nudge $\bad \gets \true$\\
if $v \neq \qry_x(S)$ then $\err \gets \err +1$\\
Return~$v$\\
%
\oracle{$\HashOracle(x)$}\\
$a,b \getsr [m]$\\
for $i = 1$ to~$k$\\
\nudge $v_i = a+i \cdot b \bmod m$\\
Return $\left(v_1,\ldots,v_k\right)$
}
}
\caption{\Cref{thm1}: Game playing argument}\label{fig:Game}
\end{figure}

%\caption{PRF game}\label{fig:prf}
\begin{figure}
\centering
\fpage{0.55}{
\hpagess{0.5}{0.35}
{
$\experimentv{\ExpPRF{F}{B}}$\\
$K \getsr \calK $\\
$\rho \getsr \Func{\univ,[m]}$\\
$b \getsr \bits$\\
$b' \getsr B^\calO$\\
Return $[b = b']$\\
}
{
$\oracle{\calO \smallskip(x)}$\\
if $ b = 1$ then\\
\nudge Return $F_K(x)$\\
Return $\rho(x)$\\
}
}
\caption{PRF security notion}\label{fig:prf}
\end{figure}

%\caption{Non-adaptive adversary $D$ simulating $\game{4}(A)$} \label{fig:D}
\begin{figure}
\centering
\fpage{0.35}
{
$\adversaryv{D(S, \pubaux)}$\\[4pt]
$c \gets 0$\\%, $\calX \gets \emptyset$\\
$\calC \gets \emptyset$; $\err \gets 0$\\
$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
Run $A(\pubaux)$\\
When $A$ asks $\TestOracle(\qry_x)$:\\
\nudge if $x \in \mathcal{C}$ then Return $\bot$\\
\nudge $\calC \gets \calC \cup x$\\
\nudge $c \gets c+1$\\
\nudge $r \gets 0$\\
\nudge if $c \in \mathcal{I}$\\
\nudge \nudge $r \gets 1$\\
\nudge \nudge $\err \gets \err + 1$\\
\nudge Return $r$\\
When $A$ halts:\\
\nudge Return $\bot$
}
\caption{Zero-query adversary $D$} \label{fig:D}
\end{figure}
